### 2016-07-01 finalText/intro.tex
Preliminary Thesis Version Completed

\chapter{Introduction}\label{chap:intro}
Brief overview of the report:

In Chapter~\ref{chap:intro}, I will present a conceptual background to the problem at hand, exposing the background that surrounds it~\ref{sec:intro_back}, the motivation for the desired solution~\ref{sec:intro_mot}, its objectives~\ref{sec:intro_obj} and, lastly, the people that will help me achieve them~\ref{sec:intro_people}.

In Chapter~\ref{chap:theorBack}, the theoretical foundations will be layed out. Section~\ref{sec:tb_basicCon} presents the basic concepts of Machine Learning, and in the following sections, the theoretical details of ANNs, RNNs and LSTMs. Section~\ref{sec:training_lstm} provides a quick explanation of the training algorithm that will be used in the final solution, which will be outlined in Section~\ref{sec:propSol}.

In Chapter~\ref{chap:earlyWork} I will present some of the work that I have already concluded.

Finally, in Chapter~\ref{chap:workPlan}, the work plan for the Dissertation work is detailed as \emph{tasks} in Section~\ref{sec:wp_tasks_td}, and their temporal arrangement is pictured in a Gantt chart in Section~\ref{sec:wp_tasks_gantt}. Furthermore, the description of the Hardware and Software resources that I will be utilizing during the course of my work is done in Section~\ref{sec:wp_sh}

@@

In order to parallelize the computations to the fullest extent, a solution is to port it both to a Graphics Processing Unit (GPU) or even a Field-Programmable Gate Array (FPGA), but the porting process is not entierely automatic and to have the least performance drop possible, it has to be explicitly programmed in CUDA/OpenCL for GPUs, and a Hardware Description Language for FPGAs, with an increasing level of complexity and low-level details. Therefore, it is necessary to provide frameworks that can allow an FPGA to quickly reconfigure itself to run these kind of networks on demand, for a particular task that requires them, achieving a lower computation time, and unburdening the CPU from running it, thus saving performance for running other tasks related with the Operating System, for instance. Furthermore, when processing an incoming stream of highly dimensional data, or with high throughput, a CPU solution might not be scalable, and could benefit greatly from a dedicated hardware implementation.

@@

\begin{itemize}
    \item \textbf{Supervisor} -- The \href{https://sigarra.up.pt/feup/pt/func\_geral.formview?p\_codigo=210963}{Professor João Canas Ferreira}, auxiliary professor at the Faculty of Engineering of the University of Porto.
    \item \textbf{Second Supervisor} -- \href{http://www.cl.cam.ac.uk/~ijpdmt2/}{Ivo Timóteo}, MSc, a Computer Science PhD candidate at Cambridge University, UK, in the field of Artificial Inteligence.
\end{itemize}

>>>>

\chapter{Introduction}\label{chap:intro}

In this work, a hardware implementation of an LSTM Neural Network is presented, along with a proposal for a digital circuit that performs on-chip training. In the reference example, the proposed hardware network was 195 times
faster than the reference software implementation. The training convergence, although simulated, is not conclusive.

@@

In order to parallelize the computations to the fullest extent, a solution is to port it both to a Graphics Processing Unit (GPU) or even a Field-Programmable Gate Array (FPGA), but the porting process is not entirely automatic and to have the least performance drop possible, it has to be explicitly programmed in CUDA/OpenCL for GPUs, and a Hardware Description Language for FPGAs, with an increasing level of complexity and low-level details. Therefore, it is necessary to provide frameworks that can allow an FPGA to quickly reconfigure itself to run these kind of networks on demand, for a particular task that requires them, achieving a lower computation time, and unburdening the CPU from running it, thus saving performance for running other tasks related with the Operating System, for instance. Furthermore, when processing an incoming stream of highly dimensional data, or with high throughput, a CPU solution might not be scalable, and could benefit greatly from a dedicated hardware implementation.

@@

\begin{itemize}
    \item \textbf{Supervisor} -- The \href{https://sigarra.up.pt/feup/pt/func\_geral.formview?p\_codigo=210963}{Professor João Canas Ferreira}, auxiliary professor at the Faculty of Engineering of the University of Porto.
    \item \textbf{Second Supervisor} -- \href{http://www.cl.cam.ac.uk/~ijpdmt2/}{Ivo Timóteo}, MSc, a Computer Science PhD candidate at Cambridge University, UK, in the field of Artificial Intelligence.
\end{itemize}

\section{Overview of the Document}\label{sec:intro_overview}
Chapter~\ref{chap:theorBack}, the theoretical foundations will be layed out. Section~\ref{sec:tb_basicCon} presents the basic concepts of Machine Learning, and in the following sections, the theoretical details of ANNs, RNNs and LSTMs. Section~\ref{sec:training_lstm} provides a quick explanation of the training algorithm that will be used in the final solution, which will be outlined in Section~\ref{chap:propSol}.

In Chapter~\ref{chap:propSol} the proposed architecture of the hardware LSTM network is explained in detail, as well as details related to each of its constituent blocks.

Finally, in Chapter~\ref{chap:results}, I present the results achieved with the hardware network of Chapter~\ref{chap:propSol}.

\textbf{Disclaimer}: since this is a very innovative work, I will not present here any Verilog source code to protect my Intellectual Property. However, you can ask permission to have it by \href{mailto:ee11126@fe.up.pt}{emailing me}.
